Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
prop4 fixed.

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. Let $p$ and $q$ be adjacent vertices of $G^{n, \ell}$, if there are at least $n$ simple paths of length
    exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
    $P{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
\end{proposition}

>>>>

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. The
    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
    $P^{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
\end{proposition}
